Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-12 ICPP-19/communications.tex
label_parser

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
	\todo[inline]{SKumar: How about this?  For simplicity, we assume throughout the paper that tasks do not have any intermediate memory requirement. Hence, amount of memory required by a task is equal to its communication volume.}
	\todo[inline]{Skumar2LED: Actually adding internal memory requirement will make NP-completeness proof straightforward. I started with this problem ;).}
	For simplicity, we assume in all of this paper that the
	amount of memory required by a task is proportional to its
	communication time, and without loss of generality we consider
	that memory size of a task is equal to its communication time.

@@

		\todo[inline]{SKumar: Do we need to mention here separately that memory requirement is equal to communication volume? I think no. right?}
		As \textit{Transfer time = Latency + (Comm Volume)/Bandwidth}. For simplicity, we consider  transfer time is same as communication volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}). Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for different memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
		\subsection{HF Performance}	
		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
			\caption{Comparison of different heuristics for HF with $m_c=..$.}
			\label{fig:ratio_to_optimal_hf}
		\end{figure*}

@@

		\subsection{CCSD Performance}
		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
			\caption{Comparison of different heuristics for CCSD with $m_c=$.}
			\label{fig:ratio_to_optimal_ccsd}
		\end{figure*}

@@

			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs. This work was supported in part by the U.S. Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823. Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
		\end{acks}

>>>>

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
	For simplicity, we assume throughout he paper that tasks
	require memory only to store their input data, and thus that
	the amount of memory required by a task is proportional to its
	communication time. Without loss of generality, we consider in
	all examples of Sections~\ref{sec:theoreticalProof}
	and~\ref{sec:heuristics} that the memory requirement of a task
	is equal to its communication time.

@@

		%% \todo[inline]{SKumar: Do we need to mention here separately that memory requirement is equal to communication volume? I think no. right?}
		%% As \textit{Transfer time = Latency + (Comm Volume)/Bandwidth}. For simplicity, we consider  transfer time is same as communication volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}). Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for different memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
		\subsection{HF Performance}	
		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
			\caption{Comparison of different heuristics for HF with $m_c=176KB$.}
			\label{fig:ratio_to_optimal_hf}
		\end{figure*}

@@

		\subsection{CCSD Performance}
		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
			\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.}
			\label{fig:ratio_to_optimal_ccsd}
		\end{figure*}

@@

			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823. Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
		\end{acks}
